Psych 254 Replication Project Analysis

### 2016-06-24 analysis.Rmd
all

passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
             "jedtan", "lampinen", "salehi")
failing <- c("sraposo", "auc", "rhiac")

@@

  print(fp)

  tryCatch(source(fp), 
           error = function(e) {
             errors <- c(errors, paste0(project_key," has an error in .R file"))
             }
           )

>>>>

passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
             "jedtan", "lampinen", "salehi")
failing <- c("smraposo", "auc", "rhiac")

@@

  print(fp)
  tryCatch(source(fp), 
           error = function(e) {
             print(e)
             }
           )
